Addition and removal energies of circular quantum dots

### 2017-09-07 Manuscript/paper.tex
Fix typo

Besides trivial cases, the HF equation is generally solved numerically using an iterative algorithm the alternates between the use of Eq.\ \eqref{eq:fock} and Eq.\ \eqref{eq:hartreefock} to successively refine an initial guess for $C_{p p'}$ until a fixed point (self-consistency) is reached.  For our calculations, we use the identity matrix as the initial guess.  When convergence is too slow, methods such as DIIS \cite{PULAY1980393,JCC:JCC540030413}, Broyden's method \cite{broyden1965class}, or even \textit{ad hoc} linear mixing can improve and accelerate convergence greatly.  For our quantum dot cases, linear mixing was more than adequate.

@@

Lastly, we note that from the above discussion it is clear that the IM-SRG is closely related to several other well-known methods of quantum chemistry such as coupled cluster theory \cite{shavitt2009many}, canonical transformation theory \cite{White:cond-mat0201346,CTreview}, the irreducible (or anti-Hermitian) contracted Schr\"odinger equation approach \cite{Mazzioti1,Mazzioti2}, and the driven similarity renormalization group method \cite{Evangelista}.  We refer the reader to Ref.\ \cite{HeikoReview} for a discussion of similarities with and differences from these approaches.

>>>>

Besides trivial cases, the HF equation is generally solved numerically using an iterative algorithm that alternates between the use of Eq.\ \eqref{eq:fock} and Eq.\ \eqref{eq:hartreefock} to successively refine an initial guess for $C_{p p'}$ until a fixed point (self-consistency) is reached.  For our calculations, we use the identity matrix as the initial guess.  When convergence is too slow, methods such as DIIS \cite{PULAY1980393,JCC:JCC540030413}, Broyden's method \cite{broyden1965class}, or even \textit{ad hoc} linear mixing can improve and accelerate convergence greatly.  For our quantum dot cases, linear mixing was more than adequate.

@@

Lastly, we note that from the above discussion it is clear that the IM-SRG is closely related to several other well-known methods of quantum chemistry such as coupled cluster theory \cite{shavitt2009many}, canonical transformation theory \cite{White:cond-mat0201346,CTreview}, the irreducible (or anti-Hermitian) contracted Schr\"odinger equation approach \cite{Mazziotti1,Mazziotti2}, and the driven similarity renormalization group method \cite{Evangelista}.  We refer the reader to Ref.\ \cite{HeikoReview} for a discussion of similarities with and differences from these approaches.
